An Abstraction-based Approach to Network Synthesis

### 2016-11-02 paper/abstraction/paper.tex
rewrite product graph formalization

\subsection{Abstract Synthesis}

\sysname builds on the Propane network configuration synthesis tool, by supporting both synthesis for and reasoning over parameterized classes of topologies and their interactions with user-specified routing policy. 
\sysname takes as input, (1) a topology abstraction in the form of a graph homomorphism annotated with logical constraints about node and edge mutliplicities, and (2) a domain-specific routing policy that consists of a mapping from predicates matching various classes of traffic, to a list of ranked constraints on the paths traffic matching the predicate should prefer to take through the network.

@@

\section{Configuration Synthesis}
\label{sec:compilation}

@@

\ryan{TODO: this was copied from previous paper for reference}

The Product Graph is constructed by adding an edge from state $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
%
Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
%
The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each automaton that has reached a final state.
% in preferences are achieved from each policy automaton for every node in the product construction.
%
We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
%
For a Product Graph if vertex $m,n = (l, \dots) \in V'$, we say that $m$ and $n$ are shadows, written: $m \approx n$.

>>>>

\subsection{Abstract Compilation}

\sysname builds on the Propane network configuration tool, by supporting both synthesis for and reasoning over parameterized classes of topologies and their interactions with user-specified routing policy. 
\sysname takes as input, (1) a topology abstraction in the form of a graph homomorphism annotated with logical constraints about node and edge mutliplicities, and (2) a domain-specific routing policy that consists of a mapping from predicates matching various classes of traffic, to a list of ranked constraints on the paths traffic matching the predicate should prefer to take through the network.

@@

\section{Compilation}
\label{sec:compilation}

@@

The Product Graph is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
%
We add edges from the start node $s$ to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
%
The preference function $P(m)$ denotes the rank of paths through the Product Graph ending at node $m$ and is defined as $P(m) = \set{i~\vert~q_{m_i} \in F_i}$. 
%
We write $(m \leq_{rank} n)$ if $P(m) = \emptyset$ or $\min ~ P(m) \leq \min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
%
We write $m \approx n$ whenever two vertices $m,n = (l, \dots) \in V'$ share the same topology location $l$.
